Generative Simplex Mapping: Nonlinear Endmember Extraction and Unmixing for Hyperspectral Imagery

### 2024-07-15 paper/paper.tex
adding more to discussion section

>>>>

- Other potential extensions to GSM model
     - Adapt latent space  to allow for points whose barycentric coordinates sum to less than 1 in order to account for lighting effects (shouldn't matter for reflectance but would matter for radiance depending on incident light). This is the $\gamma$ factor that shows up in some of the mixing papers.
